\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-17 intro.tex
update abstract/intro

Implementors of production distributed systems use many techniques to test their systems,
such as unit testing, integration testing, stress testing, and fault injection.
In spite of extensive use of these testing methods,
many bugs that arise from subtle combinations of concurrency and failure events
are missed during testing and get exposed only after a system has been put in production.
Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money~\cite{tassey2002economic} 
and many dissatisfied customers~\cite{amazon2012aws, google2014outage}.

We interviewed engineers from the Microsoft Azure team regarding the top problems in distributed system development.
The consensus was that the most critical problem today is how to improve \emph{testing coverage} to find bugs \emph{before} a system goes in production.
The need for better testing techniques is not specific to Microsoft;
other companies, such as Amazon and Google, have acknowledged~\cite{chandra2007paxos,newcombe2015aws} that testing methodologies have to improve to be able to reason about the correctness of increasingly more complex distributed systems.

In this work, our goal is to \emph{test what is being executed}.
We present a new method for testing an implementation of a distributed system and uncovering bugs before the system is released in the wild.
We have implemented our testing method in \psharp~\cite{deligiannis2015psharp}, an extension of the mainstream language \csharp that provides
support for modeling, specification, and systematic testing of asynchronous systems.
To test a distributed system with the \psharp framework, the programmer augments the system code with three artifacts---a model of the nondeterministic execution environment of the system, a concurrent test harness that drives the system towards interesting behaviors, and safety or liveness specifications for each behavior of the system under the test harness.
The \psharp testing engine then systematically explores behaviors of the test harness and validates them against the provided specifications.

We applied our approach to test three production distributed storage systems implemented inside Microsoft for the Windows Azure cloud computing
platform: a distributed storage management system; a system for migrating data across partitions; and a big-data computing system.
We uncovered numerous bugs in these systems using our approach.
In particular, we uncovered a subtle liveness bug that was intermittently manifested during stress testing for months without being debugged.
Our testing approach uncovered this bug in a very small setting, which made it easy to examine traces, identify, and eventually fix the problem.
Our experience demonstrates that bugs in production do not need a large setting to be reproduced;
they can be reproduced in small settings with easy to understand traces.

>>>>

Developers of production distributed systems use many techniques to test their systems,
such as unit testing, integration testing, stress testing, and fault injection.
In spite of extensive use of these testing methods,
many bugs that arise from subtle combinations of concurrency and failure events
are missed during testing and get exposed only after a system has been put in production.
Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money~\cite{tassey2002economic} 
and many dissatisfied customers~\cite{amazon2012aws, google2014outage}.

We interviewed technical leaders and senior managers in the Microsoft Azure team regarding the top problems in distributed system development.
The consensus was that one of the most critical problems today is how to improve \emph{testing coverage} to find bugs \emph{before} a system goes in production.
The need for better testing techniques is not specific to Microsoft;
other companies, such as Amazon and Google, have acknowledged~\cite{chandra2007paxos,newcombe2015aws} that testing methodologies have to improve to be able to reason about the correctness of increasingly more complex distributed systems.

Arguably, the most advanced practice in industry so far appears in Amazon Web Services where ``engineers use TLA+ to prevent serious but subtle bugs from reaching production''~\ref{}. The gist of their approach is to extract high level logic from production systems, represent the logic as specification in an expressive language (such as TLA+), and verify the specification using a model checker. While highly effective, as demonstrated by the numerous successes in AWS, this approach falls short of ``verifying that executable code correctly implements the high-level specification'' and the AWS team admits that ``we are not aware of any such tools that can handle distributed systems as large and complex as those being built at Amazon''~\ref{}.

We have found high level specification is necessary but not sufficient, due to the gap between the specification and the executable code.
%that ultimately powers the distributed systems.
In this work, our goal is to bridge this gap with a new framework that makes verification techniques for high level specification directly applicable to the executable code. Our framework is different from prior approaches where the developers are required to either switch to unfamiliar special programming language~\ref{}, or manually annotate and instrument production code~\ref{}. Instead, the developers can test {\em unmodified production code} by writing test harness in our framework using familiar programming language. Based on our experiences, this significantly lowered acceptance barrier and was the key to adoption in the Microsoft Azure team.

%We present a new method for testing an implementation of a distributed system and uncovering bugs before the system is released in the wild.
We have implemented our framework in \psharp~\cite{deligiannis2015psharp}, an extension of the mainstream language \csharp that provides support for modeling, specification, and systematic testing of asynchronous systems.
To test a distributed system with the \psharp framework, the programmer augments the system code with three artifacts -- a model of the nondeterministic execution environment of the system, a concurrent test harness that drives the system towards interesting behaviors, and safety or liveness specifications for each behavior of the system under the test harness.
The \psharp testing engine then systematically explores behaviors of the test harness and validates them against the provided specifications.

So far, three distributed storage systems in the Microsoft Azure team have adopted our framework: Azure Storage vNext, Azure Table Live Migration, and Azure Service Fabric.
%a distributed storage system; a system for migrating data across partitions; and a big-data computing system.
Numerous bugs were uncovered in these systems using our approach,
including, most notably, a subtle liveness bug that was intermittently manifested during stress testing for months without being fixed.
Our testing approach uncovered this bug in a very small setting, which made it easy to examine traces, identify, and eventually fix the problem.
Our experience demonstrates that bugs in production do not need a large setting to be reproduced;
they can be reproduced in small settings with easy to understand traces.

### 2015-09-17 paper.tex
merged 5 to 4
added a draft conclusion
update abstract/intro

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism in the execution, e.g., arbitrary interleavings between event handlers and unexpected node failures.
State-of-the-art testing methods commonly used in industry today---unit, integration, and stress testing---are unable to cover many behaviors, which results in tricky bugs being missed during testing and getting exposed in production.
In this paper, we present a new approach to testing distributed storage systems.
Our approach enables the developer to \emph{test what is being executed} and is engineered to work on production code.
It significantly improves coverage of important system behaviors and allows us to discover during testing errors that are often caught after deployment.

We have used our approach to test three distributed storage systems implemented inside Microsoft for the Windows Azure cloud computing platform.
In the process, we found, reproduced, and fixed numerous bugs in these systems.
The bugs discovered by our method are exhibited by executions with subtle combination of concurrency and failures,
making them extremely difficult to find with traditional testing techniques.
An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace,
which dramatically increases the productivity of debugging.

@@

%% \section{The \psharp Systematic Testing Engine}
%% \label{sec:psharp}
%% \input{psharp}

%\section{Experience Report}
%\label{sec:exp}

@@

\section{Conclusion}
\label{sec:concl}

Draft.

>>>>

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism. Conventional testing approaches are ineffective in preventing serious but subtle bugs from reaching production. Advanced industry practice, such as AWS using formal methods~\ref{}, only verifies high level specification and falls short of checking executable code. In this paper, we present a new framework for testing distributed storage systems.
Our approach makes verification techniques for high level specification directly applicable to the executable code.
It therefore significantly improves coverage of important system behaviors and uncovers during testing subtle bugs that are often caught after deployment.

Our framework has been applied to three distributed storage systems in the Microsoft Azure platform.
In the process, numerous bugs were identified, reproduced, fixed and confirmed.
The bugs discovered by our method are exhibited by executions with subtle combination of concurrency and failures,
making them extremely difficult to find with conventional testing techniques.
An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace,
which dramatically increases the productivity of debugging.

@@

\section{Additional Case Studies}
\label{sec:cases}

@@

\section{Conclusion}
\label{sec:conclusion}

\input{conclusion}
